### 2014-04-03 ApTranscriptome_TR.Rmd
Completed analyisis to compare shape of reaction norm for all transcripts using 'RxNvarshape' function

# T-test comparing standard deviation of expression between colonies
t.test(A22.int.sd, Ar.int.sd)
```
Consistent with our hypothesis, 'Intermediate' transcripts in *Ar* are expressed over a significantly wider range of temperatures than in *A22*.

@@

```{r offset, echo=TRUE, eval=TRUE}
testset <- TPM.dt.sub[1:220, ]
testoffset <- ddply(testset, .(colony, Transcript), summarise, offset = mean(TPM))
A22meanTPM <- ddply(TPM.dt.sub, .(colony, Transcript), summarise, meanTPM = mean(TPM))

>>>>

# T-test comparing standard deviation of expression between colonies
t.test(A22.int.sd, Ar.int.sd)
```

Consistent with our hypothesis, 'Intermediate' transcripts in *Ar* are expressed over a significantly wider range of temperatures than in *A22*.

@@

```{r offset, echo=TRUE, eval=TRUE}
testset <- responsive.transcripts[1:10]
varshape.out <- ldply(responsive.transcripts, .progress = "text", RxNvarshape)

# to compare among transcripts, standardize by overall mean for each transcript

# t test
t.test(varshape.out$A22.mean, varshape.out$Ar.mean)
t.test(varshape.out$A22.slope, varshape.out$Ar.slope)
t.test(varshape.out$A22.curve, varshape.out$Ar.curve)
t.test(varshape.out$A22.wiggle, varshape.out$Ar.wiggle)
